\documentclass{article}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage[textwidth=14cm]{geometry}

\begin{document}


{\scshape\LARGE EUROPEAN BLOCKCHAIN ASSOCIATION \centering \par}
\vspace{0.4cm}
{\huge\bfseries MEMBERSHIP AGREEMENT \centering \par}
\vspace{0.8cm}


THIS MEMBERSHIP AGREEMENT (the "Agreement") is effective as of this \_\_\_\_\_
day of \_\_\_\_\_\_\_\_\_\_\_\_\_, 20\_\_\_ (the “Effective Date”) by and between the European Blockchain Association (the “European Blockchain Association”) and Member \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_(“Member”). Members of the European Blockchain Association shall be referred to collectively as the “Membership At-Large”. \\
\textbf{WHEREAS}, the European Blockchain Association (EBA) combines, synchronizes and leverages blockchain-related activities of European corporations, startups, venture capitalists, and scientific institutes. 
\textbf{WHEREAS}, the EBA serves as a superior, neutral body to aggregate and coordinate blockchain activities throughout Europe and to provide Non-European parties with a direct API into the European blockchain ecosystem;
\textbf{WHEREAS}, the European Blockchain Association has adopted bylaws calling for the creation of Membership Classes, as defined, and setting forth a governance structure (the “Bylaws”, attached to the Membership Agreement in \underline{Appendix 3: Bylaws});
\textbf{WHEREAS}, Member would like to become a Member of the European Blockchain Association in the Membership Class selected by Member on the \underline{Fee Schedule and Membership Class Selection};
NOW THEREFORE, the European Blockchain Association agrees to admit Member on the terms and consideration contained herein, and Member agrees to abide by the terms and conditions contained herein:

\section{MEMBERSHIP CLASSES}
	There shall be six (6) classes of Membership (“Membership Classes”) in the European Blockchain Association representing Members that publicly, but non-exclusively, support the Purposes of the European Blockchain Association as specified in the Bylaws:
	
\begin{longtable}{| p{.55\textwidth} | p{.45\textwidth} |}
	\hline
 	   \textbf{Membership Classes} & \textbf{Membership Fees per year, in Euros} \\ \hline\hline
 	   \textbf{1a) FULL MEMBERS w. Voting Rights - Legal entities (Startups, Corporations etc.)} &
	Startup: 2.500,- \newline Small: 15.000,- (\textless 50 staff) \newline Medium: 25.000,- (50 - 250 			staff)\newline Large: 50.000,- (\textgreater 250 staff)\newline Consulting Firms: 25.000,- \\
	\hline
		\textbf{1b) FULL MEMBERS w. Voting Rights Natural persons} & 2.500,- p.p. \\                                                                                                             	\hline
		\textbf{2a) FULL ACADEMIC MEMBERS w. Voting Rights - Legal entities (Universities, Professorships)} & 2.500,- p.p. \\                                                                                                             	\hline
		\textbf{2b) FULL ACADEMIC MEMBERS w. Voting Rights - Natural persons} & 2.500,- \\                                                                                                             	\hline
		\textbf{3a) HONORARY MEMBERS without Voting Rights - Legal entities} & No Membership Fees \\                                                                                                             	\hline
		\textbf{3b) 3b) HONORARY MEMBERS without Voting Rights Natural persons} & No Membership Fees \\                                                                                                            
	\hline
\end{longtable}

\textbf{1a) FULL MEMBERS w. Voting Rights - Legal entities (Startups, Corporations etc.)} \\

‘FULL MEMBERS w. Voting Rights - Legal entities’ shall be legal entities that agree to abide by the obligations set forth in the EBA Membership Rules, including, without limitation, the requirements set forth on Exhibit B of the EBA Membership Agreement. 
Legal entities as Full Members with Voting Rights shall be permitted to vote with the Membership At-Large, as set forth in the Bylaws. 
Legal entities as Full Members with Voting Rights are entitled to found Working Groups, and initially appoint their representatives to the Working Groups’ Steering Committee. 
Legal entities as Full Members with Voting Rights commit themselves to allocate at least one FTE to the activities of the EBA. 
‘FULL MEMBERS w. Voting Rights - Legal entities’ can be Member Participants of a Working Group (WG). These entities can participate and will have voting rights with respect to WG matters as outlined within each group's charter. 
This could include scheduling meetings and activities, access/participation in the development of all materials produced in the WG, Marketing Programs, Material development, mailing lists and wikis. \\

\textbf{1b) FULL MEMBERS w. Voting Rights - Natural persons} \\

‘FULL MEMBERS w. Voting Rights - Natural persons’ shall be individuals that agree to abide by the obligations set forth in the EBA Membership Rules, including, without limitation, the requirements set forth on Exhibit B of the EBA Membership Agreement. 
Full Members with Voting Rights as individuals shall be permitted to vote with the Membership At-Large, as set forth in the Bylaws. 
As Member Participants of a Working Group (WG), these individuals can participate and will have voting rights with respect to WG matters as outlined within each group's charter. 
This could include scheduling meetings and activities, access/participation in the development of all materials produced in the WG, Marketing Programs, Material development, mailing lists and wikis. \\

\textbf{2a) FULL ACADEMIC MEMBERS w. Voting Rights - Legal entities (Universities, Professorships etc.)}

‘FULL ACADEMIC MEMBERS w. Voting Rights - Legal entities’ shall be legal entities that agree to abide by the obligations set forth in the EBA Membership Rules, including, without limitation, the requirements set forth on Exhibit B of the EBA Membership Agreement. 
Legal entities as Full Academic Members with Voting Rights shall be permitted to vote with the Membership At-Large, as set forth in the Bylaws. Legal entities as Full Academic Members with Voting Rights are entitled to found Working Groups, and initially appoint their representatives to the Working Groups’ Steering Committee. 
Full Academic Members w. Voting Rights - Legal entities’ can be Member Participants of a Working Group (WG). These entities can participate and will have voting rights with respect to WG matters as outlined within each group's charter. 
This could include scheduling meetings and activities, access/participation in the development of all materials produced in the WG, Marketing Programs, Material development, mailing lists and wikis. \\

\textbf{2b) FULL ACADEMIC MEMBERS w. Voting Rights - Natural persons} \\

‘FULL ACADEMIC MEMBERS w. Voting Rights - Natural persons’ shall be individuals that agree to abide by the obligations set forth in the EBA Membership Rules, including, without limitation, the requirements set forth on Exhibit B of the EBA Membership Agreement. 
Full Academic Members with Voting Rights shall be permitted to vote with the Membership At-Large, as set forth in the Bylaws. 
As Member Participants of a Working Group (WG), these individuals can participate and will have voting rights with respect to WG matters as outlined within each group's charter. 
This could include including scheduling meetings and activities, access/participation in the development of all materials produced in the WG, Marketing Programs, Material development, mailing lists and wikis. \\

\textbf{3a) HONORARY MEMBERS without Voting Rights - Legal entities} \\

‘HONORARY MEMBERS without Voting Rights - Legal entities’ shall be legal entities that agree to abide by the obligations set forth in the EBA Membership Rules, including, without limitation, the requirements set forth on Exhibit B of the EBA Membership Agreement. 
Legal entities as Honorary Members without Voting Rights shall not be permitted to vote with the Membership At-Large. 
Honorary Members without Voting Rights are not permitted to join any Working Groups. \\

\textbf{3b) HONORARY MEMBERS without Voting Rights - Natural persons} \\

‘HONORARY MEMBERS without Voting Rights - Natural persons’ shall be individuals that agree to abide by the obligations set forth in the EBA Membership Rules, including, without limitation, the requirements set forth on Exhibit B of the EBA Membership Agreement. 
Individuals as Honorary  Members without Voting Rights shall not be permitted to vote with the Membership At-Large. Individuals as Honorary Members without Voting Rights are not permitted to join any Working Groups. 
They may however, be invited to sit in on meetings at the discretion of the Working Group. \\

Membership is not transferable. 
The exercise of Membership rights can not be left to another person. 
Legal entities, professorships, universities and corporations must name the natural person who will be able to exercise the rights of Membership in the Membership application. \\ 

The application for Membership must be submitted in writing, by signing the EBA Membership Agreement. 
The EBA Board of Directors decides on the admission of new Members. There is no entitlement to Membership. \\

In case prospective Members aiming to join the EBA, bring in sufficient in-kind contributions, the EBA Board of Directors can discount the Membership fee or waive the fee as appropriate, based on the in-kind contribution of the prospective Members.

\section{MEMBERSHIP RIGHTS AND OBLIGATIONS}

\subsection{Generally}

Member agrees to pay the annual fees established for its Membership Class, if any, as set forth in Exhibit B hereto, as may be amended from time to time in accordance with the Bylaws. 
Member agrees to abide by other terms relating to the payment of fees, as further specified in Section 2.4 herein. 
Any FTEs contributed by Members to work on EBA projects will be fully compensated by Member and not by the European Blockchain Association except when the board has granted a special budget for the work on the basis of a milestone-based plan submission.

\subsection{Compliance with Policies}

Members agree to abide by, and shall have all applicable rights and obligations as set forth in, the European Blockchain European Blockchain Association’s bylaws, the European Blockchain European Blockchain Association’s Intellectual Property Rights Policy (the “IPR Policy”), and all additional policies and procedures adopted by the European Blockchain Association, as may be amended from time to time in accordance with the European Blockchain Association’s bylaws.

\subsection{Compliance with Licences}

Members review, and agree to abide by, and shall have all rights and obligations as set forth in the European Blockchain Association’s Intellectual Property Rights Policy (IPR Policy), as may be amended from time to time in accordance with the EBA’s bylaws. 
Members agree to follow all licencing procedures as set forth in the European Blockchain Association’s Intellectual Property Rights Policy, unless otherwise agreed to in accordance with the EBA’s bylaws and IPR Policy.

\subsection{Late Fees / Costs and Expenses}

\subsubsection{Late Fees}

If a Member’s payment of its annual Membership dues is not fully paid within sixty (60) days of its invoice due date, a late fee representing one percent (1\%) of the delinquent Membership dues shall be added to such Membership dues, compounding monthly, commencing on the 31st day following invoice date.
 Additionally, if a Member qualifies for quarterly payment of its annual Membership dues (according to Exhibit B) and has not fully paid a payment within thirty (30) days of its invoice due date, a late fee representing one percent (1\%) of the delinquent Membership dues shall be added to such Membership dues, compounding monthly, commencing on the 31st day following invoice date.

\subsubsection{Costs and Expenses}

Each Member shall bear all of its own costs and expenses related to Membership in the European Blockchain Association including, but not limited to, compensation payable to Member’s employees and consultants that participate in the European Blockchain Association on behalf of Members, and all travel and other expenses associated with Member’s participation in European Blockchain Association meetings, conferences, and development projects.
 Except as otherwise set forth in this Agreement or in the Bylaws, Member understands and agrees that Member has no rights of reimbursement from the European Blockchain Association.

\subsection{Publicity}

\subsubsection{Press Releases}

A new Member shall assist the European Blockchain Association in publicly announcing such new Member’s Membership therein within ninety (90) days of joining the European Blockchain Association. 
A Member may make public announcements or press releases concerning its own activities as a Member.
 Unless otherwise required by law, any press release concerning a Member made by the European Blockchain Association or another Member shall be subject to that Member's prior written consent. 
 Once approved, the press release statement may be used by the European Blockchain Association and other Members for the purpose of promoting the European Blockchain Association (or such purpose as is designated in the Member's consent) and reused for such purpose until such approval is withdrawn with reasonable prior written notice. 
 Any use of a Member's name shall be subject to the applicable usage guidelines of that Member.

\subsection{Use of Name}

Members agree to comply with the then current European Blockchain Association Copyright Guidelines.

\section{TERM AND TERMINATION}

\subsection{Term}

The term of this Agreement shall begin on the Effective Date and, except as provided below, shall continue indefinitely subject to the rights of termination set forth in Section 4.2.

\subsection{Termination}

Member may terminate its Membership or be removed there from in accordance with the regulations of the bylaws. Upon termination of Member’s Membership, this Membership Agreement shall terminate.

\subsection{Survival}

In the event of termination under Section 4.2, the following shall survive and remain in effect: Sections 2.3, 4 and 5. In addition, Member shall be obligated to pay all costs, expenses and dues that accrued prior to the effective date of termination.

\section{GENERAL}

\subsection{Authority to Execute Agreement}

Member hereby represents, warrants and covenants to the European Blockchain Association that (a) it has the authority to enter into this Agreement and to perform its obligations hereunder; (b) the execution and performance of this Agreement does not and will not violate any agreement to which Member is a party or by which it is otherwise bound; and (c) when executed and delivered, this Agreement will constitute a legal, valid and binding obligation of Member, enforceable in accordance with its terms.

\subsection{No Other Licenses}

By executing this Agreement, Member neither grants nor receives, by implication, estoppel, or otherwise, any rights under any copyright, patents or other intellectual property rights of the European Blockchain Association or another Member.

\subsection{No Employment Relationship}

Nothing in this Agreement is intended to give rise to an employer-employee relationship between Member and the European Blockchain Association.

\subsection{No Warranty}

The European Blockchain Association and Member each acknowledges that,  except otherwise agreed in writing, all information provided to or by the European Blockchain Association under this agreement is provided “as is” with no warranties or conditions whatsoever, whether express, implied, statutory or otherwise, and the European Blockchain Association and Member each expressly disclaim any warranty of merchantability, noninfringement, and fitness for any particular purpose with respect to such information. 

\subsection{Limitation of Liability}

In no event will either the European Blockchain Association or Member be liable to each other or any other Member Third Party under this Agreement for the cost of procuring substitute goods or services, lost profits, lost revenue, lost sales, loss of use, loss of data or any incidental, consequential, direct, indirect, punitive, or special damages, whether or not such party had advance notice of the possibility of such losses or damages.

\subsection{Governing Law}

This Agreement shall be construed and controlled by German law without reference to conflict of law principles.

\subsection{Notices}

All notices or other communications to or upon any party shall be delivered to or at the addresses set forth on the signature page(s) hereto. For purposes of this Section, notice can include notice by written mail, electronic mail or by facsimile and shall be deemed served when sent; provided, however, that notice of a breach of this Agreement and notice of termination of this Agreement shall be given by overnight courier service or certified mail, return receipt requested. Either party may give written notice of a change of address and, after notice of such change has been received, any notice or request shall thereafter be given to such party at such changed address.

\subsection{Complete Agreement; No Waiver}

Except with respect to the European Blockchain Association’s Bylaws , IPR Policy, Antitrust Policy, the Apache License 2.0 (if applicable), and any other policies and procedures that may be adopted by the European Blockchain Association from time to time in accordance with the Bylaws, this Agreement, including all attachments, sets forth the entire understanding of the European Blockchain Association and Member and supersedes all prior agreements and understandings relating hereto, unless otherwise stated in this Agreement. 
The waiver of any breach or default will not constitute a waiver of any other right hereunder or any subsequent breach or default.

\subsection{Amendment}

Member shall be given at least thirty (30) days prior written notice of the effective date of an amendment agreed to in accordance with the Bylaws. 
No amendments, modifications or additions to or deletions from this Agreement shall be binding unless accepted in writing by authorized representatives of the European Blockchain Association and Member. 
If Member does not agree to a modification to this Agreement that was approved in accordance with the Bylaws, this Agreement and Member’s Membership in the European Blockchain Association shall be terminated.
 Amendments shall be prospective only unless otherwise agreed to by the Member and the European Blockchain Association.

\subsection{No Rule of Strict Construction}

Regardless of which party may have drafted this Agreement, no rule of strict construction shall be applied against either party. 
If any provision of this Agreement is determined by a court to be unenforceable, the parties shall deem the provision to be modified to the extent necessary to allow it to be enforced to the extent permitted by law, or if it cannot be modified, the provision will be severed and deleted from this Agreement, and the remainder of this Agreement will continue in effect.

\subsection{Counterparts}

This Agreement may be executed in one or more counterparts, each of which shall be deemed an original, but collectively shall constitute one and the same instrument.

\subsection{Compliance with Laws}

Anything contained in this Agreement to the contrary notwithstanding, the obligations of the European Blockchain Association and Member shall be subject to all laws, present and future, of any government having jurisdiction over the European Blockchain Association and Member including, without limitation, all export and re-export laws and regulations. 
It is the intention of the European Blockchain Association and Member that this Agreement and all referenced documents shall comply with all applicable laws and regulations.

\subsection{Headings}

The European Blockchain Association and Member acknowledge that the headings to the sections hereof are for reference purposes only and shall not be used in the interpretation of this Agreement.

\subsection{Assignment}

Member may not assign its rights or obligations under this Agreement without the prior written consent of the European Blockchain Association or as otherwise set forth in the Bylaws. 
For purposes of this Agreement, an assignment shall be deemed to include a transfer or sale of all or substantially all of the business of Member, or a merger, consolidation or other transaction that results in a change in control of Member.

\subsection{Force Majeure}

Neither the European Blockchain Association nor Member shall be liable hereunder by reason of any failure or delay in the performance of its obligations hereunder on account of strikes, shortages, riots, insurrection, fires, flood, storm, explosions, acts of God, war, governmental action, labor conditions, earthquakes or any other cause which is beyond the reasonable control of such party.

\subsection{General Construction}

As used in this Agreement, the plural form and singular form each shall be deemed to include the other in all cases where such form would apply. “Includes” and “including” are not limiting, and “or” is not exclusive.

\subsection{Independent Contractors}

The relationship of the European Blockchain Association and Member established by this Agreement is that of independent contractors. 
This Agreement does not give either party the power to direct and control the day to day activities of the other, constitute the parties as partners, joint venturers, co-owners, principal-agent or otherwise participants in a joint or common undertaking, or, except as expressly provided herein, allow either party to create or assume any obligation on behalf of the other for any purpose whatsoever.

\subsection{Order of Precedence}

Notwithstanding anything else to the contrary in this Agreement or in any other agreement entered into with the European Blockchain Association, in the case of the conflict between the terms of this Agreement and any other agreement except for the EBA’s Intellectual Property Rights Policy, the terms of this Agreement shall control. 
Notwithstanding anything else to the contrary in this Agreement, in the case of the conflict between the terms of this Agreement and the terms of the EBA’s Intellectual Property Rights Policy, the terms of the EBA’s Intellectual Property Rights Policy shall control.

\subsection{Dispute Arbitration}

All Members including Members serving on the Board of Directors agree to binding resolution by the Blockchain Arbitration Forum in the case of disputes.
 Any dispute, controversy or claim arising under, out of or relating to this contract and any subsequent amendments of this contract, including, without limitation, its formation, validity, binding effect, interpretation, performance, breach or termination, as well as non-contractual claims, shall be referred to and finally determined by arbitration in accordance with the WIPO Arbitration Rules. 
 The arbitral tribunal shall consist of a sole arbitrator. 
 The place of arbitration shall be Munich, Germany.
  The language to be used in the arbitral proceedings shall be English. 
  The dispute, controversy or claim shall be decided in accordance with the laws of Germany. 
  If requested by one party duly in advance, the hearing shall take place via telephone conference.
 

\newpage

{\scshape\LARGE FEE SCHEDULE AND MEMBERSHIP CLASS SELECTION \centering \par}

\begin{longtable}{| p{.45\textwidth} | p{.35\textwidth} | p{.20\textwidth} |}
	\hline
 	   \textbf{Membership Classes} & \textbf{Membership Fees per year, in Euros} & \textbf{Check to indicate desired level of Membership} \\ \hline\hline
 	   \textbf{1a) FULL MEMBERS w. Voting Rights - Legal entities (Startups, Corporations etc.)} &
	Startup: 2.500,- \newline Small: 15.000,- (\textless 50 staff) \newline Medium: 25.000,- (50 - 250 			staff)\newline Large: 50.000,- (\textgreater 250 staff)\newline Consulting Firms: 25.000,- &  \\
	\hline
		\textbf{1b) FULL MEMBERS w. Voting Rights Natural persons} & 2.500,- p.p. & \\                                                                                                             	\hline
		\textbf{2a) FULL ACADEMIC MEMBERS w. Voting Rights - Legal entities (Universities, Professorships)} & 2.500,- p.p. & \\                                                                                                             	\hline
		\textbf{2b) FULL ACADEMIC MEMBERS w. Voting Rights - Natural persons} & 2.500,- &  \\                                                                                                             	\hline
		\textbf{3a) HONORARY MEMBERS without Voting Rights - Legal entities} & No Membership Fees &  \\                                                                                                             	\hline
		\textbf{3b) 3b) HONORARY MEMBERS without Voting Rights Natural persons} & No Membership Fees & \\                                                                                                            
	\hline
\end{longtable}

\noindent BE SURE TO PLACE A CHECK IN THE TABLE ABOVE INDICATING YOUR DESIRED LEVEL OF MEMBERSHIP \\

The Fees may be amended from time to time in accordance with the Bylaws and shall, from the date of such amendment, replace the previously existing Fees. Any such change shall not require re-execution of this Agreement. If such amendment has been duly approved, Member agrees to payment of such Fees.  \\

Annual Membership dues are levied on a yearly basis. Following acceptance and signing of this agreement, members will be billed for the membership dues selected in the table above and will be billed for membership dues on a recurring basis thereafter.\\

Important: Annual Membership dues for natural persons may be waived on an individual basis subject to approval by the EBA board of directors. Legal entities are generally not eligible for such waivers. Natural persons may apply for a fee waiver on the basis of a commitment to make in-kind contributions to the EBA in lieu of paying the Annual Membership dues. If granted, fee waivers are issued on a one-year renewable basis.\\

 \CheckBox[width=1em]{I petition the EBA board of directors to waive my annual membership dues for one year from the date of this agreement. I commit to make in-kind contributions to the EBA in lieu of paying the Annual Membership dues within one year.} \\

\newpage

{\scshape\LARGE OFFICIAL BANK ACCOUNT OF THE EUROPEAN BLOCKCHAIN ASSOCIATION \centering \par}

\begin{center}
  \uline{\bfseries The following bank details may be used for all EBA official business including but not limited to the payment of membership fees:}\\
\end{center}

\noindent {\bfseries Deutsche Skatbank\\}
Zweigniederlassung der\\
VR-Bank Altenburger Land eG\\
Altenburger Strasse 13\\
04626 Schmölln\\

\noindent {\bfseries IBAN\\}
DE94 8306 5408 0004 2273 60\\

\noindent {\bfseries BIC\\}
GENODEF1SLR\\

{\scshape\LARGE OFFICIAL BLOCKCHAIN ACCOUNTS OF THE EUROPEAN BLOCKCHAIN ASSOCIATION \centering \par}

\begin{center}
  \uline{\bfseries The following blockchain addressses may be used for all EBA official business parallel to the fiat bank details above. Payments can be sent directly to the domain eublas.crypto using a wallet compatible with Unstoppable Domains. This includes but is not limited to the payment of membership fees:}\\
\end{center}

\noindent {\bfseries Unstoppable Domain\\}
eublas.crypto\\

\noindent {\bfseries ETH\\}
0x1DCC19852C2681E2dfF10231686Bf99EDffEa7bE\\

\noindent {\bfseries BTC\\}
bc1qef8ruptzrzh5cves349n448ktet5y8wr2qhrln\\

\noindent {\bfseries XLM\\}
GBH2BRVWXRTINTHTSIKJKDLRE6ESS33YTYVT3JEVDNZT3IIWFTBBM4DQ\\

\newpage
\textbf{Legal Entities (ONLY Membership Type 1a, 2a, 3a)}
\begin{longtable}{| p{.35\textwidth} | p{.65\textwidth} |}
	\hline
	\newline 
	\textbf{Name of the Institution} \newline & \\
	\hline	
	\newline 
	\textbf{Address} \newline & \\
	\hline	
	\newline 
	\textbf{Country} \newline & \\
	\hline	
	\newline 
	\textbf{Attention} \newline & \\
	\hline	
	\newline 
	\textbf{Name of the Representative} \newline & \\
	\hline	
	\newline 
	\textbf{Title of the Representative} \newline & \\
	\hline	
	\newline 
	\textbf{E-Mail} \newline & \\
	\hline	
	\newline 
	\textbf{Telephone} \newline & \\
	\hline	
	\newline 
	\textbf{Ethereum Address} \newline & \\
	\hline	
\end{longtable}
\vspace{1cm}


By signing this document, you agree that you have read the bylaws and agree with the governance process of the European Blockchain Association e. V.

\vspace{2cm}

Location, Date: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

\vspace{2cm}

Signature: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

\newpage

\textbf{Natural Person (ONLY Membership Type 1b, 2b, 3b)}
\begin{longtable}{| p{.35\textwidth} | p{.65\textwidth} |}
	\hline
	\newline 
	\textbf{Name and Surname} \newline & \\
	\hline	
	\newline 
	\textbf{Address} \newline & \\
	\hline	
	\newline 
	\textbf{Country} \newline & \\
	\hline
	\newline 
	\textbf{E-Mail} \newline & \\
	\hline	
	\newline 
	\textbf{Telephone} \newline & \\
	\hline
	\newline 
	\textbf{GitHub Username (for Developers only} \newline & \\
	\hline	
	\newline 
	\textbf{Ethereum Address} \newline & \\
	\hline	
\end{longtable}
\vspace{3cm}


By signing this document, you agree that you have read the bylaws and agree with the governance process of the European Blockchain Association e. V.

\vspace{2cm}

Location, Date: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

\vspace{2cm}

Signature: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_	


















\end{document}